---
title: "Cookie Quality using Gage R&R"
author: "Leslie, Oliver, Maya, Maya, Sparsh"
date: 2025-04-21
output:
  github_document:
    toc: true
---

## Set Up

```{r setup}
library(tidyverse)
library(modelr)
library(broom)
```

## Background Research

-   What’s your question?
-   What data do you plan to use to answer this question?
-   What challenges do you anticipate encountering?
-   What level of complexity of final product are you aiming for?
-   What figures / tables do you anticipate producing?

## **Import file**

```{r import-task}
filename_cookie <- "./data/results_gage_R_R.csv"
## NOTE: No need to edit
df_cookie <-
  read_csv(
    filename_cookie,
  )

df_cookie
```

## **Conduct Initial Checks - EDA**

```{r intial-checks}
summary(df_cookie)

head(df_cookie)
```

#### Quantify sources of uncertainty

-   How reputable is the source? How well-documented are their data-collection procedures? What potential errors might be in the data? What factors could contribute to missingness in the data?
-   How were the data collected? Is it a random sample? A non-random sample? A full population?
-   To the extent possible, report all estimates with confidence / prediction / tolerance intervals. If not possible, clearly explain why it is not possible to provide intervals and document what sources of uncertainty are not quantified. \#### Obeservations
-   ....
-   ....

## **Conduct ANOVA**

### Circumference

```{r anova-circumference}
cookie.cir <- aov(Circumference ~ Index + Tray + Fridge + Cheap + Chocolate_chips + Data_taker, data = df_cookie)

summary(cookie.cir)
```

```{r homoscedasticity-circumference}
par(mfrow=c(2,2))
plot(cookie.cir)
par(mfrow=c(1,1))
```

### Height

```{r anova-height}
cookie.hei <- aov(Height ~ Index + Tray + Fridge + Cheap + Chocolate_chips + Data_taker, data = df_cookie)

summary(cookie.hei)
```

```{r homoscedasticity-height}
par(mfrow=c(2,2))
plot(cookie.hei)
par(mfrow=c(1,1))
```

### Length

```{r anova-length}
cookie.len <- aov(Length ~ Index + Tray + Fridge + Cheap + Chocolate_chips + Data_taker, data = df_cookie)

summary(cookie.len)
```

```{r homoscedasticity-length}
par(mfrow=c(2,2))
plot(cookie.len)
par(mfrow=c(1,1))
```

### Width

```{r anova-width}
cookie.wid <- aov(Width ~ Index + Tray + Fridge + Cheap + Chocolate_chips + Data_taker, data = df_cookie)

summary(cookie.wid)
```

```{r homoscedasticity-width}
par(mfrow=c(2,2))
plot(cookie.wid)
par(mfrow=c(1,1))
```

### Weight

```{r anova-weight}
cookie.wei <- aov(Weight ~ Index + Tray + Fridge + Cheap + Chocolate_chips + Data_taker, data = df_cookie)

summary(cookie.wei)
```

```{r homoscedasticity-weight}
par(mfrow=c(2,2))
plot(cookie.wei)
par(mfrow=c(1,1))
```

## **Tukey Honestly Significant Difference**

```{r Tukey HSD1}
tukey.cir<-TukeyHSD(cookie.cir)
tukey.hei<-TukeyHSD(cookie.hei)
tukey.len<-TukeyHSD(cookie.len)
tukey.wid<-TukeyHSD(cookie.wid)
tukey.wei<-TukeyHSD(cookie.wei)

tukey.cir
tukey.hei
tukey.len
tukey.wid
tukey.wei
```

## **Mean of Outputs**

```{r mean}
mean.cir <- df_cookie %>%
  group_by(Index, Cheap) %>%
  summarise(
      cir = mean(Circumference)
  )

mean.hei <- df_cookie %>%
  group_by(Index, Chocolate_chips) %>%
  summarise(
      hei = mean(Height)
  )

mean.len <- df_cookie %>%
  group_by(Index, Cheap) %>%
  summarise(
      len = mean(Length)
  )

mean.wid <- df_cookie %>%
  group_by(Index, Cheap) %>%
  summarise(
      wid = mean(Width)
  )

mean.wei <- df_cookie %>%
  group_by(Index,Cheap) %>%
  summarise(
      wei = mean(Weight)
  )

mean.cir
mean.hei
mean.len
mean.wid
mean.wei
```

## **Graph Time**

```{r graph1}

df_cookie %>%
  ggplot(aes(x = as.factor(Index), y = Circumference, color = as.factor(Cheap))) +
  geom_point(size = 2, shape = 1, position = position_jitter(width = 0.15, height = 0)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.4) +
  stat_summary(fun = mean, geom = "point", size = 3, shape = 18) +
  labs(
    x = "Cookie Index Number",
    y = "Circumference (cm)",
    color = "Cheap or Expensive",
    title = "Cookie Circumference by Index and Price Category"
  ) +
  theme_minimal(base_size = 13) +
  scale_color_manual(values = c("steelblue", "tomato")) +
  theme(
    axis.text.x = element_text(angle = 0, hjust = 0.5),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "top"
  )
```

```{r graph2}

df_cookie %>%
  ggplot(aes(x = as.factor(Index), y = Height, color = as.factor(Chocolate_chips))) +
  geom_point(size = 2, shape = 1, position = position_jitter(width = 0.15, height = 0)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.4) +
  stat_summary(fun = mean, geom = "point", size = 3, shape = 18) +
  labs(
    x = "Cookie Index Number",
    y = "Height (mm)",
    color = "Number of Chocolate Chips",
    title = "Cookie Height by Chocolate Chip Count"
  ) +
  scale_color_viridis_d(option = "C", end = 0.85) +
  theme_minimal(base_size = 13) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "top",
    plot.title = element_text(face = "bold", hjust = 0.5)
  )
```

```{r graph3}

df_cookie %>%
  ggplot(aes(x = as.factor(Index), y = Length, color = as.factor(Cheap))) +
  geom_point(size = 2, shape = 1, position = position_jitter(width = 0.15, height = 0)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.4) +
  stat_summary(fun = mean, geom = "point", size = 3, shape = 18) +
  labs(
    x = "Cookie Index Number",
    y = "Length (mm)",
    color = "Price Category",
    title = "Cookie Length by Price Category"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "top",
    plot.title = element_text(face = "bold", hjust = 0.5)
  )
```

```{r graph4}

df_cookie %>%
  ggplot(aes(x = as.factor(Index), y = Width, color = as.factor(Cheap))) +
  geom_point(size = 2, shape = 1, position = position_jitter(width = 0.15, height = 0)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.4) +
  stat_summary(fun = mean, geom = "point", size = 3, shape = 18) +
  labs(
    x = "Cookie Index Number",
    y = "Width (mm)",
    color = "Price Category",
    title = "Cookie Width by Price Category"
  ) +
  theme_minimal(base_size = 13) +
  scale_color_manual(values = c("#5F9EA0", "#C68642")) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "top",
    plot.title = element_text(face = "bold", hjust = 0.5)
  )
```

```{r graph5}

df_cookie %>%
  ggplot(aes(x = as.factor(Index), y = Weight, color = as.factor(Cheap))) +
  geom_point(size = 2, shape = 1, position = position_jitter(width = 0.15, height = 0)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.4, color = "black") +
  stat_summary(fun = mean, geom = "point", size = 3, shape = 18, color = "black") +
  labs(
    x = "Cookie Index Number",
    y = "Weight after Baking (grams)",
    color = "Price Category",
    title = "Cookie Weight by Price Category"
  ) +
  scale_color_manual(values = c("#4C6D8C", "#D4A373")) +
  theme_minimal(base_size = 13) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "top",
    plot.title = element_text(face = "bold", hjust = 0.5)
  )
```
